EasyMerge - A New Tool for Code Clones Refactoring

### 2014-03-09 paper/paper.tex
fixing references

Previous research shows that a significant fraction (between 7\% and 23\%) of the code in a typical software system has been cloned \cite{baker} \cite{roy}. Many code clones
in code bases are unnecessary duplications. 
Code duplication can be a significant drawback, leading to bad design, and increased probability of bug occurrence and propagation. As a result, it can significantly
increase maintenance cost, and form a barrier for software evolution. By detecting, categorizing,
and removing code clones, we can produce easier to understand, cleaner, and more reusable code.

@@

\section{Background}

>>>>

Previous research shows that a significant fraction (between 7\% and 23\%) of the code in a typical software system has been cloned \cite{baker} \cite{roy1}. Many code clones
in code bases are unnecessary duplications. 
Code duplication can be a significant drawback, leading to bad design, and increased probability of bug occurrence and propagation. As a result, it can significantly
increase maintenance cost, and form a barrier for software evolution. By detecting, categorizing,
and removing code clones, we can produce easier to understand, cleaner, and more reusable code.

@@

\section{Background}
Roy and Cordy has done a great work \cite{roy2}
